Supplementary Material

### 2019-12-10 papers/ACL2020/manynames.tex
[ACL2020] small things

We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn.
Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
We ran all the \mn data (response sets) through our verification, with two exceptions: 
response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
They were asked to judge the ``adequacy''\footnote{
	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
} of each name on a 3-point scale: ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
If they did not select ``adequate'' they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
Lastly, annotators were asked to judge which names were likely intended for the same object, through an interface where they would assign the same color to names for the same object.
%% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.

>>>>

We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn.
Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
We ran all the \mn data (response sets) through our verification, with two exceptions: 
response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~1 in the supplementary material).
They were asked to judge the ``adequacy''\footnote{
	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
} of each name on a 3-point scale: ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
If they did not select ``adequate'' they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
Lastly, annotators were asked to judge which names were likely intended for the same object, through an interface where they would assign the same color to names for the same object.
%% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.

### 2019-12-10 papers/ACL2020/related.tex
[ACL2020] small things

\paragraph{The ManyNames dataset}
The \mn dataset (MN, Anonymous, under review) which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
Its vocabulary of all names has 7,970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these we collected a new layer of verification annotations on top of \mn, as follows.

>>>>

\paragraph{The ManyNames Dataset}
The \mn dataset (MN, Anonymous, under review) which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
Its vocabulary of all names has 7,970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these we collected a new layer of verification annotations on top of \mn, as follows.

### 2019-12-10 papers/ACL2020/supplementary.tex
[ACL2020] small things

\paragraph{Task interface and instructions}
The task interface is shown in Figure~\ref{fig:verification-interface}.
We provided (and clarified by means of explanation and visual examples, not show in the image) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
The buttons in the interface all contained suitable pictorial representations to facilitate learning the task.
We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons and some of the highlighted terms in the task headings.
The hover text of the coloring/clustering task contained a visual example of a completed color grid.
Feedback from annotators suggested that the task interface was intuitive, and they generally enjoyed doing our tasks.
\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{images/verification-interface.pdf}
	\caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
	\label{fig:verification-interface}
\end{figure*}

@@

\paragraph{Approval/rejection, compensation and bonus}
Upon task approval, annotators were awarded \$0.50.
Annotators who scored 100\% accuracy on our quality controls (ignoring ones that no annotator did correctly) received a bonus of \$0.15, as we announced in the instructions for extra incentive.
After every round we blocked annotators with average accuracy below 90\%, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of the \mn data.
Approval/rejection was decided on a much lower threshold of 70\% accuracy, and with various mechanisms in place for more leniency, e.g., the first task below this threshold would be approved nonetheless; and any task below this threshold would be approved if the annotator's average accuracy was above 90\%.
We rejected less than 2\% of the tasks.

>>>>

\paragraph{Task interface and Instructions}
The task interface is shown in Figure~\ref{fig:verification-interface}.
We provided (and clarified by means of explanation and visual examples, not show in the image) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
The buttons in the interface all contained suitable pictorial representations to facilitate learning the task.
We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons and some of the highlighted terms in the task headings.
The hover text of the coloring/clustering task contained a visual example of a completed color grid.
Feedback from annotators suggested that the task interface was intuitive, and they generally enjoyed doing our tasks.
\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{images/verification-interface.pdf}
	\caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
	\label{fig:verification-interface}
\end{figure*}

@@

\paragraph{Approval/Rejection, Compensation and Bonus}
Upon task approval, annotators were awarded \$0.50.
Annotators who scored 100\% accuracy on our quality controls (ignoring ones that no annotator did correctly) received a bonus of \$0.15, as we announced in the instructions for extra incentive.
After every round we blocked annotators with average accuracy below 90\%, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of the \mn data.
Approval/rejection was decided on a much lower threshold of 70\% accuracy, and with various mechanisms in place for more leniency, e.g., the first task below this threshold would be approved nonetheless; and any task below this threshold would be approved if the annotator's average accuracy was above 90\%.
We rejected less than 2\% of the tasks.
